Opportunistic attachment assembles plant-pollinator networks: A walk through of the analysis

### 2017-05-18 analysis/writeup/writeup.tex
lots of small cahnges for reproducibility

\hlcom{## occ.date is significant}
\hlstd{pol.lm.cv.quant} \hlkwb{<-} \hlkwd{lqmm}\hlstd{(}\hlkwc{fixed}\hlstd{=cv} \hlopt{~} \hlstd{occ.date} \hlopt{+} \hlstd{r.degree,} \hlkwc{random}\hlstd{=}\hlopt{~}\hlnum{1}\hlstd{,}
                        \hlkwc{group}\hlstd{= GenusSpecies,}
                        \hlkwc{data}\hlstd{=pol.cv}\hlopt{$}\hlstd{lm.data,}
                        \hlkwc{control}\hlstd{=}\hlkwd{list}\hlstd{(}\hlkwc{LP_max_iter}\hlstd{=}\hlnum{10}\hlopt{^}\hlnum{4}\hlstd{))}
\hlstd{pol.sum.boot.quant} \hlkwb{<-} \hlkwd{summary.boot.lqmm}\hlstd{(}\hlkwd{boot}\hlstd{(pol.lm.cv.quant,}
                                             \hlkwc{R}\hlstd{=}\hlnum{100}\hlstd{))}
\end{alltt}
\begin{verbatim}
## Quantile 0.5 
##                  Value Std. Error lower bound upper bound Pr(>|t|)    
## (Intercept)  3.7160065  0.0854433   3.5464685      3.8855  < 2e-16 ***
## occ.date     0.7040012  0.2454156   0.2170433      1.1910  0.00504 ** 
## r.degree    -0.0010938  0.0032266  -0.0074960      0.0053  0.73533    
## scale        0.2869339  0.0185467   0.2501333      0.3237  < 2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\hlcom{## for poisson models}
\hlstd{mods.splines.log} \hlkwb{<-} \hlkwd{lapply}\hlstd{(poi.ys, calcSpine,} \hlkwc{calc.log}\hlstd{=}\hlnum{TRUE}\hlstd{)}
\end{alltt}
\begin{verbatim}
## $info
## [1] 0
## 
## $smoothingParameters
##    mu     v 
## 11000 10000 
## 
## $info
## [1] 0
## 
## $smoothingParameters
##    mu     v 
## 11000 10000 
## 
## $info
## [1] 0
## 
## $smoothingParameters
##    mu     v 
## 11000 10000
\end{verbatim}
\begin{alltt}
\hlkwd{names}\hlstd{(mods.splines.log)} \hlkwb{<-} \hlstd{poi.ys}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## no effect of ypr on robustness}
\hlstd{mod.ypr} \hlkwb{<-} \hlkwd{lmer}\hlstd{(Robustness} \hlopt{~} \hlstd{ypr}
                \hlopt{+} \hlstd{(}\hlnum{1}\hlopt{|}\hlstd{Site)} \hlopt{+} \hlstd{(}\hlnum{1}\hlopt{|}\hlstd{Year),}
                \hlkwc{data}\hlstd{=res[}\hlopt{!}\hlkwd{is.na}\hlstd{(res}\hlopt{$}\hlstd{ypr),])}
\hlkwd{summary}\hlstd{(mod.ypr)}
\end{alltt}
\begin{verbatim}
## Linear mixed model fit by REML t-tests use Satterthwaite approximations
##   to degrees of freedom [lmerMod]
## Formula: Robustness ~ ypr + (1 | Site) + (1 | Year)
##    Data: res[!is.na(res$ypr), ]
## 
## REML criterion at convergence: -166.9
## 
## Scaled residuals: 
##      Min       1Q   Median       3Q      Max 
## -1.99009 -0.62116 -0.07289  0.56358  2.37929 
## 
## Random effects:
##  Groups   Name        Variance  Std.Dev.
##  Site     (Intercept) 2.395e-03 0.048943
##  Year     (Intercept) 5.091e-05 0.007135
##  Residual             4.842e-03 0.069583
## Number of obs: 80, groups:  Site, 14; Year, 8
## 
## Fixed effects:
##              Estimate Std. Error        df t value Pr(>|t|)    
## (Intercept)  0.333299   0.016943 10.950000  19.671 6.85e-10 ***
## ypr          0.000965   0.004133 32.430000   0.233    0.817    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##     (Intr)
## ypr -0.374
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\hlcom{## occ.date is significant}
\hlstd{pol.lm.cv.quant} \hlkwb{<-} \hlkwd{lqmm}\hlstd{(}\hlkwc{fixed}\hlstd{=cv} \hlopt{~} \hlstd{occ.date} \hlopt{+} \hlstd{r.degree,} \hlkwc{random}\hlstd{=}\hlopt{~}\hlnum{1}\hlstd{,}
                        \hlkwc{group}\hlstd{= GenusSpecies,}
                        \hlkwc{data}\hlstd{=pol.cv}\hlopt{$}\hlstd{lm.data,}
                        \hlkwc{control}\hlstd{=}\hlkwd{list}\hlstd{(}\hlkwc{LP_max_iter}\hlstd{=}\hlnum{10}\hlopt{^}\hlnum{4}\hlstd{))}
\hlstd{pol.sum.boot.quant} \hlkwb{<-} \hlkwd{summary.boot.lqmm}\hlstd{(}\hlkwd{boot}\hlstd{(pol.lm.cv.quant,}
                                             \hlkwc{R}\hlstd{=}\hlnum{100}\hlstd{))}
\end{alltt}
\begin{verbatim}
## Quantile 0.5 
##                  Value Std. Error lower bound upper bound Pr(>|t|)    
## (Intercept)  3.7160065  0.0767061   3.5638049      3.8682  < 2e-16 ***
## occ.date     0.7040012  0.2686421   0.1709569      1.2370  0.01016 *  
## r.degree    -0.0010938  0.0026191  -0.0062906      0.0041  0.67712    
## scale        0.2869339  0.0191043   0.2490269      0.3248  < 2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\hlcom{## for poisson models}
\hlstd{mods.splines.log} \hlkwb{<-} \hlkwd{lapply}\hlstd{(poi.ys, calcSpine,} \hlkwc{calc.log}\hlstd{=}\hlnum{TRUE}\hlstd{)}
\end{alltt}
\begin{verbatim}
## $info
## [1] 0
## 
## $smoothingParameters
##    mu     v 
## 11000 10000 
## 
## $info
## [1] 0
## 
## $smoothingParameters
##    mu     v 
## 11000 10000
\end{verbatim}
\begin{alltt}
\hlkwd{names}\hlstd{(mods.splines.log)} \hlkwb{<-} \hlstd{poi.ys}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## no effect of ypr on robustness}
\hlstd{mod.ypr} \hlkwb{<-} \hlkwd{lmer}\hlstd{(Robustness} \hlopt{~} \hlstd{ypr}
                \hlopt{+} \hlstd{(}\hlnum{1}\hlopt{|}\hlstd{Site)} \hlopt{+} \hlstd{(}\hlnum{1}\hlopt{|}\hlstd{Year),}
                \hlkwc{data}\hlstd{=res[}\hlopt{!}\hlkwd{is.na}\hlstd{(res}\hlopt{$}\hlstd{ypr),])}
\hlkwd{summary}\hlstd{(mod.ypr)}
\end{alltt}
\begin{verbatim}
## Linear mixed model fit by REML t-tests use Satterthwaite approximations
##   to degrees of freedom [lmerMod]
## Formula: Robustness ~ ypr + (1 | Site) + (1 | Year)
##    Data: res[!is.na(res$ypr), ]
## 
## REML criterion at convergence: -165.6
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.9965 -0.6661 -0.0787  0.5873  2.3210 
## 
## Random effects:
##  Groups   Name        Variance  Std.Dev.
##  Site     (Intercept) 0.0022317 0.04724 
##  Year     (Intercept) 0.0001305 0.01143 
##  Residual             0.0049176 0.07013 
## Number of obs: 80, groups:  Site, 14; Year, 8
## 
## Fixed effects:
##              Estimate Std. Error        df t value Pr(>|t|)    
## (Intercept) 3.320e-01  1.703e-02 1.127e+01  19.501 4.91e-10 ***
## ypr         8.384e-04  4.231e-03 3.627e+01   0.198    0.844    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##     (Intr)
## ypr -0.386
\end{verbatim}
\end{kframe}
\end{knitrout}
